The Eclipse Integrated Computational Environment

### 2019-07-24 src/ack.tex
Committing first draft of ICE paper.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Added separate acknowledgements file.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\section{Acknowledgements}
The authors are grateful for the assistance and support of the following people
and institutions without which this work would not have been possible.

\textbf{FIXME!}

This work has been supported by the US Department of Energy, Offices of Nuclear
Energy (DOE-NE) and Energy Efficiency and Renewable Energy (DOE-EERE), and by
the ORNL Undergraduate Research Participation Program, which is sponsored by
ORNL and administered jointly by ORNL and the Oak Ridge Institute for Science
and Education (ORISE). This work was also supported in part by the Oak Ridge
National Laboratory Director's Research and Development Fund. ORNL is managed by
UT-Battelle, LLC, for the US Department of Energy under contract no.
DE-AC05-00OR22725. ORISE is managed by Oak Ridge Associated Universities for
the US Department of Energy under contract no. DE-AC05-00OR22750.

\textbf{LDRD ACK?!}

>>>>

The authors are grateful for the assistance and support of the following
people and institutions without whom this work would not have been
possible. This includes many people who directly contributed to the
project, either in its early days as ``NiCE'' or once it moved to
Eclipse, including Ronald Allen, Andrew Belt, David E.
Bernholdt, Tim Bohn, Erica Grant, Mike Guidry, John M. Hetrick III, Forest Hull, 
Sebastien Jourdain, JiSoo Kim, Allison Koenecke, Fangzhou Lin, Eric J. Lingerfelt, Greg
Lyon, Tony McCrary, Elizabeth Piersall, Neeti
Pokhriyal, Adrian Sanchez, Claire Saunders, Nick Stanish, Matthew Wang, and
Scott Wittenberg. The support of both the Nuclear Energy Advanced Modeling and
Simulation (NEAMS) and Consortium for Simulation of Light Water Reactors (CASL)
programs is also greatly appreciated. The authors would like to acknowledge the
special contribution of the Eclipse Foundation, the Eclipse Community, the
Eclipse Science Working Group, and our many colleagues who use and contribute
to open-source projects in the Eclipse ecosystem.

Finally, the development team is especially grateful to Barney Maccabe,
David Pointer, and John Turner of ORNL for their
endless support and advocacy for this work.

This work has been supported by the DOE, Offices of
Nuclear Energy (DOE-NE) and Energy Efficiency and Renewable Energy
(DOE-EERE) and by the ORNL Undergraduate Research Participation
Program, which is sponsored by ORNL and administered jointly by ORNL and
the Oak Ridge Institute for Science and Education (ORISE). This work was
also supported in part by the ORNL Laboratory Directed
Research and Development Program. ORNL is managed by UT-Battelle LLC for under
contract DE-AC05-00OR22725. ORISE is managed by Oak Ridge Associated
Universities for the US Department of Energy under contract no.
DE-AC05-00OR22750.
